MSF_Groupwork-NBA_shotlog

### 2016-10-11 MSFGroupwork-NBAHotHand.Rmd
df2 read csv updated. and working on regression

###Introduction
I   What is your theme or research question?
a. Hot Hand Theory (Artemis)
b. Defender Proximity Analysis (Reza)
c. Shot Clock Pressure  (Alex)
d. Close Game Effect - Small Margin affecting the scoring rate 
e. Home Advantage (Alex is working in this point)  
f. Fatigue Effect (Quarter Heat Rate)  
g. Shooting Percentage (James)
h. Fatigue Effect (Number of Rest Day)  
i.

@@

#we need to change the format of some of the columns to 'Character'

@@

>>>>

###Introduction
I   What is your theme or research question?
a. Hot Hand Theory (Artemis)
b. Defender Proximity Analysis (Reza)
c. Shot Clock Pressure  (Alex)
d. Close Game Effect - Small Margin affecting the scoring rate 
e. Home Advantage (Alex is working in this point)  
f. Fatigue Effect (Quarter Heat Rate)  
g. Shooting Percentage (James)
h. Fatigue Effect (Number of Rest Day)  
i. Regression Analysis (Alex)

@@

df2<- read.csv("shot_logs1010.csv")

#we need to change the format of some of the columns to 'Character'
#get rid off 'attach()'
#get rid off column X in shot logs1010 file

@@

```{r}
#Regression Analysis
colnames(df2)

linreg_fgm <-lm(FGM ~ GAME_ID1 + MATCHUP+LOCATION+W+FINAL_MARGIN+SHOT_NUMBER+ PERIOD+GAME_CLOCK+  SHOT_CLOCK+  DRIBBLES+ TOUCH_TIME+SHOT_DIST+PTS_TYPE+ SHOT_RESULT+ CLOSEST_DEFENDER + CLOSEST_DEFENDER_PLAYER_ID + CLOSE_DEF_DIST +PTS+player_name+ player_id+HOME_TEAM+AWAY_TEAM+WINNER, df2 )

summary(linreg_fgm)

linreg_fgm2 <-lm(FGM ~ GAME_ID1 + MATCHUP+LOCATION+W+FINAL_MARGIN+SHOT_NUMBER+ PERIOD+GAME_CLOCK+  SHOT_CLOCK+  DRIBBLES+ TOUCH_TIME+SHOT_DIST+PTS_TYPE+ SHOT_RESULT+ CLOSEST_DEFENDER + CLOSEST_DEFENDER_PLAYER_ID + CLOSE_DEF_DIST +PTS+player_name+ player_id+HOME_TEAM+AWAY_TEAM+WINNER, df2 )

summary(linreg_fgm)
